---
title: "R lottery"
output: html_notebook
---

What the project is about.
The project is about explaining the probabilities of winning a lottery.

What your goal is in this project.
The goal is so that to educate the lottery addicts about buying more tickets would not increase the probabilities much towards winning the lottery.
load resources 

```{r}
library(readr)
library(purrr)
```

load the data
```{r}
lottery <- read_csv("649.csv")
```
Write a factorial function and a combination function
```{r}
factorial <- function (n){
  result <- 1
  for(i in 1:n) {
    result <- result * n
  }
  return(result)
}

combination <- function (n, k) {
  factorial(n)/factorial(k)/factorial(n-k)
}
```

practice using list in pmap
```{r}
data1 <- c(1, 3, 5)
data2 <- c(2, 4, 6)
data3 <- c(8, 9, 7)

unnamed_list <- list(data1,data2,data3)
#how to access the values
unnamed_list[[1]]
unnamed_list[[1]][3]
sum_on_each_position <- pmap(unnamed_list,function(x,y,z) x+y+z)
#make the results easier to read
unlist(sum_on_each_position)

named_list <- list(first = data1, second= data2, third = data3)
#how to access the values
named_list[[1]]
named_list[[1]][3]
named_list$first
named_list$first[3]
#can't use pmap!! Giving a name is bad???
pmap(named_list,function(x,y,z) x+y+z)
named_list$first[1] + named_list$secon[1] + named_list$third[1]

```
Inside the app, the user inputs six different numbers from 1 to 49.
Under the hood, the six numbers will come as an R vector and serve as an input to our function.
The engineering team wants us to write a function that prints:
the number of times the combination selected occurred in the Canada data set and
the probability of winning the big prize in the next drawing with that combination.
```{r}
num_cols <- map_chr(1:6, function (x) paste("NUMBER DRAWN ", x))
input <- c(1,2,3,4,5,6)
vector1 <- c(1,2,3,3)
vector2 <- c(2,4,3,1)
vector3 <- c(3,2,3,2)
vector4 <- c(4,2,3,4)
vector5 <- c(5,1,4,5)
vector6 <- c(6,4,2,6)
vector_list <- list(vector1, vector2, vector3, vector4,vector5, vector6)

to_vector <- function (v1,v2,v3,v4,v5,v6){
  c(v1,v2,v3,v4,v5,v6)
}
check_historical_occurence <- function (vectors, input) {
  result <- sum(unlist(map(vectors, function(x) setequal(x,input))))
  ifelse(result > 0, TRUE, FALSE)
}
for(vector in vectors_temp){
  print(vector)
}

history <- list(lottery$`NUMBER DRAWN 1`,lottery$`NUMBER DRAWN 2`,lottery$`NUMBER DRAWN 3`,lottery$`NUMBER DRAWN 4`,lottery$`NUMBER DRAWN 5`,lottery$`NUMBER DRAWN 6`)
vectors <- pmap(history, to_vector)

input1 <- c(1,2,3,4,5,6)
input2 <- c(3, 12, 11, 14, 41, 43)
check_historical_occurence(vectors, input1)
check_historical_occurence(vectors, input2)

probability_winning_next_prize <- 1/combination(49,6)
```

The probability of winning a lottery using one set of numbers is 0.00000001.

```{r}
multi_ticket_probability <- function (n) {
  sprintf('The probability of winning using %.0f tickets is %.6f%%',n, n/combination(49,6)*100)
}

multi_ticket_probability(1)
n_tickets <- c(1, 10, 100, 10000, 1000000, 6991908, 13983816)
map(n_tickets, multi_ticket_probability)

```
write a function to caculate the probability of winning smaller prices, as matching 3, 4, 5 numbers.
```{r}
probability_less_6 <- function (n){
  result <- 1/combination(49,n)
  sprintf("The probability of winning %.0f number is %.6f%%",n, result*100)
}

probability_less_6(3)
probability_less_6(4)
probability_less_6(5)
```

